P4Query: Static Analyser Framework for P4

### 2021-03-26 publications/The_tool_intro/paper.tex
pub: title
pub: removed accent from email
tool_intro: some typo

	\title{P4Query - an analyser framework for P4}

	\author{Dániel Lukács}
	\email{dlukács@inf.elte.hu}
	\orcid{0000-0001-9738-1134}
	\affiliation{%
		\institution{ELTE, Eötvös Loránd University, Faculty of Informatics}
        \country{Hungary}
        \city{Budapest}
	}

@@

  The expressive power of Gremlin is proved in another recent work~\cite{yamaguchi}: the authors store C code information in Neo4j, and define recurring vulnerability patterns as Gremlin queries. Using this apporach, the authors discovered 18 previously unknown vulnerabilities in the Linux kernel.

@@

\paragraph{Gremlin API}
In the tool architecture described in this section, we use a Gremlin graph database as storage backend (knowledge graph). Gremlin is a compositional query language and API that is implemented by many large-scale graph databases. This makes it possible to change graph implementations with almost no modification to the P4Query code base. In earlier work~\cite{icai20}, we also profiled a few graph backends for control flow traverals, and verified that -- apart from the initial overhead -- in-memory graph databases have comparable performance to built-in memory manipulation.

>>>>

	\title{P4Query: Static Analyser Framework for P4}

	\author{Dániel Lukács}
	\email{dlukacs@inf.elte.hu}
	\orcid{0000-0001-9738-1134}
	\affiliation{%
		\institution{ELTE, Eötvös Loránd University, Faculty of Informatics}
        \country{Hungary}
        \city{Budapest}
	}

@@

  The expressive power of Gremlin is proved in another recent work~\cite{yamaguchi}: the authors store C code information in Neo4j, and define recurring vulnerability patterns as Gremlin queries. Using this approach, the authors discovered 18 previously unknown vulnerabilities in the Linux kernel.

@@

\paragraph{Gremlin API}
In the tool architecture described in this section, we use a Gremlin graph database as storage backend (knowledge graph). Gremlin is a compositional query language and API that is implemented by many large-scale graph databases. This makes it possible to change graph implementations with almost no modification to the P4Query code base. In earlier work~\cite{icai20}, we also profiled a few graph backends for control flow traversals, and verified that -- apart from the initial overhead -- in-memory graph databases have comparable performance to built-in memory manipulation.
